Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-20 paper/paper.tex
Refactoring seeds folder
pass on intro and es section

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements will entail sensible changes in runtime
engines~\cite{kangax}; changes that could lead to errors. Finding bugs
on JS engines is an important problem.

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional bugs in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across configurations. They use this technique since 2002 and have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, some of which are security bugs.
Cross-engine differential testing checks correctness by comparing the
output produced by \emph{different} engines on a given
input~\cite{patra2016learning}. The availability on the web of public
implementations of JS engines (see Table~\ref{tab:engines}) and test
suites makes this bug-finding approach very appealing.

%% WHAT WE DID
This paper reports the results of a study we conducted to (i) assess
the reliability of existing JS engines and to (ii) evaluate the
importance of different factors when using DT for bug finding. More
precisely, we analyzed the impact of two orthogonal factors in the use
of DT: test mining and fuzzing. The first dimension, test mining,
considers the effect that \js{} test files mined from the repository
of a given open-source engine have in detecting functional bugs in
other engines. The second dimension, fuzzing, considers the impact of
fuzzing the mined files in bug detection.
%% WHAT WE FOUND
To sum, we found that \Fix{...}

@@

\section{ES6 design}
\label{sec:es6-design}
The EcmaScript is a language specification maintained by 
a committee called TC39 (Technical Committee) that follows 
standard rules proposed by ISO/ETC JTC 1 - 
Information Technology since 1996~\cite{es6-website}.
Every year, a new version of EcmaScript (the latest version is ES2017) adds
new features and minor fixes for the language. \Fix{discutir mais
  sobre isso}

@@

@@

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and other suites.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 45,144 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 51,815 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

  A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
  \Fix{discuss}

>>>>

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations (see
Section~\ref{sec:es6-design}). It is natural to expect that such
improvements will entail sensible changes in runtime
engines~\cite{kangax}; changes that could lead to errors. Even small
changes can have a large impact in practice. For example, in October
2014 a new attribute added to the Array datatype caused a bug that
resulted in MS Outlook web not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. To
sum, finding bugs on JS engines is an important problem.

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find bugs
in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across configurations. They use this technique since 2002 and have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, some of which are security bugs.
Cross-engine differential testing, in contrast, checks correctness by
comparing the output produced by \emph{different} engines on a given
input~\cite{patra2016learning}. The availability of public
implementations of JS engines (see Table~\ref{tab:engines}) and test
suites makes this bug-finding approach appealing.

%% WHAT WE DID
This paper reports the results of a study we conducted to (i) assess
the reliability of existing JS engines and to (ii) evaluate the
importance of different factors when using DT. More precisely, we
analyzed the impact of two orthogonal factors in DT: test mining and
fuzzing. The first factor, test mining, considers the effect that
\js{} test files mined from the repositories of open-source engines
have in detecting functional bugs in other engines. The second factor,
fuzzing, considers the impact in bug detection of fuzzing these files.
%% WHAT WE FOUND
To sum, we found that \Fix{...}

@@

\section{EcmaScript}
\label{sec:es6-design}

ECMAScript (\es{}) emerged with the goal to standardize variants of
JavaScript, such as Netscape's JavaScript and Microsoft's JScript. The
\es{} specification is maintained by the TC39~\cite{tc39-github}
technical committee under the regulation of Ecma
International~\cite{es6-website}.  Every year, a new version of the
specification is delivered with new features and minor fixes. The
canonical spec today is
ES6~\cite{ecmas262-spec-repo,ecmas262-spec}. Features of these
versions and supporting engines can be found elsewhere~\cite{kangax}.

\subsection{Engines Design}

@@

\subsection{Implementation-Dependent Behavior}
\label{sec:imp-dep-behavior}

The \es{} spec uses the label ``implementation-dependent'' to indicate
cases where each engine developer can decide how to implement some
aspect of a functionality. In these cases, execution may differ from
engine to engine. One of the reasons implementation-dependent behavior
exists is to enable compiler optimizations. For example, the
\mcodeid{for-in} loop does not clearly specify the iteration
order~\cite{for-in-undefined} and different engines capitalize on
that.

@@

\subsection{Undefined Behavior}
\label{sec:undef-behavior}

Undefined behavior is not a feature of the C
language~\cite{c-undefined}.

\Mar{mention strict?}

\subsection{Unintentional Discrepancies}

It is worth to recall that there is no formal specification for \es{};
the specification is written in natural language. As such, differences
in behavior from one engine to another, other than those mentioned
above (Sections~\ref{sec:imp-dep-behavior}
and~\ref{sec:undef-behavior}), can occur. But these discrepancies are
not acceptable.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 45,144 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 51,815 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

  % A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  % quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  % devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
